Interpretable Machine Learning

### 2019-07-03 chunks/story-wines.Rmd
finalize talk

@@

## How can we solve this problem? {.emphasizedabit}

- Hand-written rules
- Statistical Model
- Machine Learning

@@

## {data-background=../images/dog-car.gif data-background-size=contain}

>>>>

## Disclaimer: I am NOT a wine expert!

```{r, out.width = "50%"}
knitr::include_graphics("../images/wine-expert.png")
```

@@

# How can we solve this problem?

@@

## {data-background=../images/make-it-rain.gif data-background-size=contain}
